The importance of fidelity in the scheduling of Redox Flow Batteries.

### 2018-11-02 Paper/main.tex
Update main.tex

%Added by Diarmid
\usepackage{siunitx}

@@

At present, revenue from arbitrage on the wholesale electrical price is not in itself sufficient to justify BESS investment, and the deployment of grid scale BESS is dominated by projects that have won contracts for short term stability services tendered by National Grid. For example, \SI{500}{\mega\watt} of BESS capacity won contracts for the T-4 2020/21 capacity market (CM) auction, and \SI{200}{\mega\watt} of BESS capacity won enhanced frequency response (EFR) contracts. The majority of successful BESS applicants for the EFR auction also have CM contracts. \sol{This is a bit parochial, the same is regarding BESS elsewhere (i.e. the big Tesla abttery). We need to widen the story out to make the paper relevant outside the UK}

@@

Schedule optimisation is often performed by posing the objective function and constraints as linear algebraic terms, and using an algorithm such as Simplex to determine the maximum or minimum of the objective function. This approach, known as linear programming (LP) is efficient because the optimum value for each variable will either lie at the maximum or minimum of a permitted value, making a search of the interior unnecessary.

\cite{Johnston2015} used a LP formulation to optimise the scheduling of a VRFB installed at a wind farm. The objective was to maximise revenue on the wholsesale electrical market while satisfying the frequency response obligations (constraints) of the wind installation\sol{what did they find?}. \cite{Vaca2017} looked at a similar application but compared the payback period for VRFB and supercapacitor installations with a hybrid system. In both studies, a cost of degradation in \pound per unit energy throughput was applied as a coefficient to ESS power variables in the objective function. This approach discourages the performance of arbitrage below a certain threshold price differential \sol{why is this note worthy?}.

A full system schedule optimisation problem was posed by \cite{Chen2012} to assess the benefit of a VRFB in a microgrid with a load, PV, wind and dispatchable micro-generation. When the micro-grid was isolated, the objective was to minimise the start-up and running costs of micro-generators used to back up the renewable power output. The authors used a mixed-integer LP (MILP) approach, where the integer variables were required to factor start-up costs. Additional global constraints were required to guarantee system reliability \sol{are these reliability constraints interesting? Yes, if one is interested in a whole system!}.

\cite{Gomes2017}  studied the application of a VRFB in order to cope with stochastic deviations from the forecast exports of wind and solar power into a day ahead market. A two stage optimisation was applied, and LP was used to optimise the VRFB schedule in the first stage.

@@

The key innovation of the present work is the introduction of a RFB schedule optimisation framework posed in terms of current-density rather than power. This allows the separation of the voltaic and coulombic components of the power input/output. Using the introduced framework, three novel augmentations (add-ons?) to the typical scheduling problem are posed while maintaining an easily computable problem:

>>>>

%Added by Diarmid
\usepackage{siunitx}
\usepackage{hyperref}
    \hypersetup{colorlinks=true,linkcolor=green}

@@

At present, revenue from arbitrage on the wholesale electrical price is not in itself sufficient to justify BESS investment \cite{Johnston2015}. and the deployment of grid scale BESS is dominated by projects that have won contracts for short term stability services tendered by National Grid. For example, \SI{500}{\mega\watt} of BESS capacity won contracts for the T-4 2020/21 capacity market (CM) auction, and \SI{200}{\mega\watt} of BESS capacity won enhanced frequency response (EFR) contracts. The majority of successful BESS applicants for the EFR auction also have CM contracts. \sol{This is a bit parochial, the same is regarding BESS elsewhere (i.e. the big Tesla battery). We need to widen the story out to make the paper relevant outside the UK}

@@

Schedule optimisation is often performed by posing a linear programming (LP) problem \cite{}. In this method, the objective function and the constraints on the system are expressed as linear algebraic terms. On the resulting geometric space, the optimum is guaranteed to lie on a vertex, hence a costly search of the whole surface is not required.

\cite{Johnston2015} used a LP formulation to optimise the scheduling of a VRFB installed at a wind farm. The objective was to maximise revenue on the wholesesale electrical market and the frequency response market, while always maintaining an energy reserve in order to meet . By repeating this process at different energy and power ratings, the authors found that the economically optimal VRFB rating for the \SI{50}{\mega\watt} wind farm was \SI{5.3}{\mega\watt} and \SI{3}{\mega\watt\hour}. This illustrates the point made above regarding the poor economics of wholesale market arbitrage - the optimal RFB rating is dictated by the frequency market revenue and the reserve energy requirement. Increasing the capacity of the VRFB in order to perform additional wholesale market arbitrage is not economical. The authors also suggested that a hybrid system may be suitable, as the economically optimal VRFB operates in a narrow SOC window when providing frequency regulation, with the remaining SOC held in reserve for large frequency deviations that occur infrequently.

This thread was picked up by \cite{Vaca2017} who compared a hybrid system consisting of a VRFB and a supercapacitor with the individual systems. They found that the hybrid system was the optimal choice, with the VRFB providing the energy capacity and the supercapacitor the low cost power capacity.

It is worth noting that both \cite{Johnston2015,Vaca2017} assume a higher cost of energy capacity than power capacity for the VRFB. This contradicts economic modelling of system costs by \cite{Viswanathan2014,Ha2015Estimatingstorage}, where the energy cost is markedly lower.

\cite{Johnston2015} and \cite{Vaca2017} apply a cost of degradation in \pound per unit energy throughput as a coefficient to ESS power variables in the objective function. This approach captures an important consideration in electrical price arbitrage using ESS - that there is a threshhold price differential below which the degradation cost outweighs the revenue. In both works the capital cost of the ESS and the degradation cost are included, but the residual value at project end is not counted. \cite{Dufo-Lopez2009} present a more detailed economic model for various ESS used to increase the value of wind power sold into a day-ahead market. The residual value of the ESS at the end of the project is pro-rated according to the number of cycles performed as a fraction of the expected cycle life, and discounted to a net present value. The schedule optimisation in this work is not as thorough as the LP approaches of  \cite{Johnston2015,Vaca2017}; the day is divided into two peak periods where the ESS is discharged and two off-peak where it is charged, and the boundaries of the periods may be varied iteratively to find an apparent optimum.

A full system LP schedule optimisation problem was posed by \cite{Chen2012} to assess the benefit of a VRFB in a microgrid with a load, PV, wind and dispatchable micro-generation. When the micro-grid was isolated, the objective was to minimise the start-up and running costs of micro-generators used to back up the renewable power output. The authors used a mixed-integer LP (MILP) approach, where the integer variables were required to factor start-up costs. Additional global constraints were required to guarantee system reliability \sol{are these reliability constraints interesting? Yes, if one is interested in a whole system!}.

\cite{Gomes2017}  studied the application of a VRFB in order to cope with stochastic deviations from the forecast exports of wind and solar power into a day ahead market. A two stage optimisation was applied, and LP was used to optimise the VRFB schedule based on the forecast  in the first stage.

@@

The key innovation of the present work is the introduction of a RFB schedule optimisation framework posed in terms of current-density rather than power. This allows the separation of the voltaic and coulombic components of the power input/output. Using the introduced framework, three novel augmentations \emph{(add-ons?)} to the typical scheduling problem are posed while maintaining an easily computable problem:
